---
title: "R Notebook"
output: html_document
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
```{r}

```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}

```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.



```{r}
```
# Installing the packages


```{r}

install.packages("data.table")        # install it
library(data.table)
install.packages("dplyr")
library(dplyr)
library(tidyr)
```

# Loading and previewing our dataset

```{r}

df <- read.csv("./advertising (1).csv")

```

# Previewing the six top rows in our dataset
```{r}
# We use the head(df) to preview the first 6 rows of our dataset
head(df)
```


# Handling Missing Data with R

```{r}
# Lets Identify missing data in your dataset

print(is.na(df))


```

# Checking missing values
```{r}

print(colSums(is.na(df)))

```
# Dimensions of our data


```{r}
print(dim(df))
```

# Getting the names of our rows
```{r}
data <- df
rownames(data)
```
# Getting the column names of our dataset


```{r}
print(colnames(df))
```
# UNIVARIATE DATA ANALYSIS


```{r}
#  Measures of Central Tendency
mean_income <- mean(df$Area.Income)

print(mean_income)

```
```{r}

# Mean daily internet usage
mean_daily_internet <- mean(df$Daily.Internet.Usage)

print(mean_daily_internet)


```
```{r}
mean_time_spent_on_site <- mean(df$Daily.Time.Spent.on.Site)

print(mean_time_spent_on_site)


```
```{r}
# Mean daily internet usage
median_daily_internet <- median(df$Daily.Internet.Usage)

print(median_daily_internet)
```
```{r}

min_time_spent_on_site <- min(df$Daily.Time.Spent.on.Site)

print(min_time_spent_on_site)

```
```{r}

max_daily_internet <- max(df$Daily.Internet.Usage)

print(max_daily_internet)

```
```{r}

#Quantile time spent on site
quantile_time <- quantile(df$Daily.Time.Spent.on.Site)

print(quantile_time)


```
```{r}
# Find the variance of the distance using the var() function as shown below

variance_daily_internet_usage <- var(df$Daily.Internet.Usage)

print(variance_daily_internet_usage)

```
```{r}
#Standard deviation of age

std_daily_internet_usage_age <- sd(df$Daily.Internet.Usage)

print(std_daily_internet_usage_age)
```
```{r}
daily_internet_usage_frequency <- table(df$Daily.Internet.Usage)

daily_internet_usage_frequency
```
```{r}

# Then applying the barplot function to produce its bar graph

barplot(daily_internet_usage_frequency)

```

# Bivariate and Multivariate



```{r}
#### Covariance

age <- df$Age
internet_usage_frequency <- df$Daily.Internet.Usage

cov(age,internet_usage_frequency)


```
```{r}

daily_internet_usage <- df$Daily.Internet.Usage

area_income <- df$Area.Income

cov(daily_internet_usage,area_income)

```
```{r}

# Correlation Coefficient

city <- df$City

state <- df$State

cor(city,state )



```
```{r}

# There is a very low correlation
cor(daily_internet_usage,area_income)
```
```{r}
# Creating the scatter plot using eruptions and waiting
# ---
#
plot(daily_internet_usage, area_income, xlab="Daily Internet Usage", ylab="Area Income")
```
```{r}

```
```{r}

```
Click the **Knit and Open Document** to build and preview an output.