---
title: "R Notebook"
output: html_document
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
```{r}

```
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}

```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.



```{r}
```
# Installing the packages


```{r}

install.packages("data.table")        # install it
library(data.table)
install.packages("dplyr")
library(dplyr)
library(tidyr)
```

# Loading and previewing our dataset

```{r}

df <- read.csv("./advertising (1).csv")

```

# Previewing the six top rows in our dataset
```{r}
# We use the head(df) to preview the first 6 rows of our dataset
head(df)
```


# Handling Missing Data with R

```{r}
# Lets Identify missing data in your dataset

is.na(df)


```

# Checking missing values
```{r}

colSums(is.na(df))

```
# Dimensions of our data


```{r}
dim(df)
```

# Getting the names of our rows
```{r}
data <- df
rownames(data)
```
# Getting the column names of our dataset


```{r}
colnames(df)
```
```{r}

```
```{r}

```
```{r}

```
```{r}

```
```{r}

```
```{r}

```
Click the **Knit and Open Document** to build and preview an output.